---
title: "Package nwfscDeltaGLM: simulation example"
author: "NWFSC-assess"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package nwfscDeltaGLM: simulation example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Install package and set working directory

```{r install}
# Install package
install.packages("devtools", repos = "http://cran.us.r-project.org")
library("devtools")
install_github("nwfsc-assess/nwfscDeltaGLM")
  
# Load package
library(nwfscDeltaGLM)
```

## Load data and strata

```{r load}
Sim_List = SimSimple(
  MeanEncounter = 0.5,
  Nyears = 10,
  Nstrata = 15,
  Nvessels = 4,
  Obsperyear = 175,
  sigmaV = rep(0, 2),
  sigmaVY = rep(1, 2),
  sigmaS = rep(1, 2),
  sigmaY = rep(1, 2),
  sigmaSY = rep(1, 2),
  sigmaResid = 1
  )

masterDat = Sim_List[["DF"]]

strata.limits = data.frame(
  STRATA = LETTERS[1:15],
  NLat = seq(1.5, 15.5, 1),
  SLat = seq(0.5, 14.5, 1),
  MinDepth = 0,
  MaxDepth = 100,
  stringsAsFactors = FALSE
  )
```

### Modify species names
```{r}
species = "Simulated_Species"
names(masterDat)[which(names(masterDat)=="SPECIES_WT_KG")] = species
masterDat = cbind(masterDat, AREA_SWEPT_MSQ=masterDat$AREA_SWEPT_HA*1e4)
```

### Generate covariates that aren't important (i.e., not in the true operating model)
```{r}
Covariates = list(positive=TRUE, binomial=TRUE)
nX.binomial = 1
nX.pos = 1
X.bin = matrix( rnorm(nrow(masterDat)*nX.binomial, mean=0, sd=1), ncol=nX.binomial)
X.pos = matrix( rnorm(nrow(masterDat)*nX.pos, mean=0, sd=1), ncol=nX.pos)
```

## Run data processing function
This looks for an object named \code{masterDat} in the global environment,
```{r}
DataList = processData(masterDat = masterDat, strata.limits = strata.limits, X.bin=X.bin, X.pos=X.pos)
```

## Run model

### Define settings for this run
```{r}
mcmc.control = list(chains=3, thin=1, burnin=100, iterToSave=200)

modelStructure1 = list("StrataYear.positiveTows"="zero", 
      "VesselYear.positiveTows"="random2", 
      "StrataYear.zeroTows"="zero", 
      "VesselYear.zeroTows"="random2", 
      "Vessel.positiveTows"="zero", 
      "Vessel.zeroTows"="zero", 
      "Catchability.positiveTows"="one", 
      "Catchability.zeroTows"="zero", 
      "year.deviations"="fixed", 
      "strata.deviations"="fixed")

modelStructure2 = list("StrataYear.positiveTows"="zero", 
      "VesselYear.positiveTows"="zero",
      "Vessel.positiveTows"="random2",
      "StrataYear.zeroTows"="zero",
      "VesselYear.zeroTows"="zero",
      "Vessel.zeroTows"="random2",
      "Catchability.positiveTows"="one",
      "Catchability.zeroTows"="zero",
      "year.deviations"="fixed",
      "strata.deviations"="fixed")
```

### Run model 
Create a list that could be used to hold additional models,

```{r, eval=FALSE}
fitted_models = list()
fitted_models[[1]] = fitDeltaGLM(datalist=DataList, 
          likelihood = "gamma", 
          modelStructure=modelStructure1, 
          mcmc.control=mcmc.control, 
          covariates=Covariates, Species=species)
fitted_models[[2]] = fitDeltaGLM(datalist=DataList, 
          likelihood = "gamma", 
          modelStructure=modelStructure2, 
          mcmc.control=mcmc.control, 
          covariates=Covariates, 
          Species=species)
```





